%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Leadership and Volunteer Work}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
    % \cventry
    % {\empty} % Affiliation/role
    % {EverydayBME - Co-Founder} % Organization/group
    % {2019 --- Present | Worldwide} % Location
    % {} % Date(s)
    % {
    %     \vspace{-.3cm}
    %     \begin{cvitems} % Description(s) of experience/contributions/knowledge
    %         \item {Design and aggregate digital storybooks of Biomedical science (researchers, students, etc.) over the world. Worked with BMESDiversity and Whitaker Foundation.}
    %     \end{cvitems}
    % }

    \cvpresentation
    {Mentor new developers in contributing to open-source software.} % Role
    {Google Summer of Code - Mentor} % Title
    {2022 --- Present | Worldwide} % Location
    {} % Date(s)
    {\empty}
    {\empty}
    \vspace{-.9cm}   
    
    \cvpresentation
    {Design and aggregate digital storybooks of Biomedical science (researchers, students, etc.) over the world. Worked with BMESDiversity and Whitaker Foundation to highlight under-represented groups in STEM.} % Role
    {EverydayBME - Co-Founder} % Title
    {2019 --- Present | Worldwide} % Location
    {} % Date(s)
    {\empty}
    {\empty}
    \vspace{-.9cm}
    
    \cvpresentation
    {Planned and implement a summer leadership and advocacy program for under-served AAPI youth. Also involved in raising over \$5000 as a non profit organization.} % Role
    {AAMPLIFY 501(C) - Director of Leadership} % Title
    {2017 --- Present | San Francisco, CA} % Location
    {} % Date(s)
    {\empty}
    {\empty}
    \vspace{-.9cm}
    
    \cvpresentation
    {Plan events for collaborations between engineering, medicine and public health. Arduino workshop, Machine Learning in Healthcare workshop, and Electronic Health Records for Engineering workshop.} % Role
    {Engineering \& Medicine Exchange - Co-Founder} % Title
    {2016 --- 2017 | JHU} % Location
    {} % Date(s)
    {\empty}
    {\empty}
    \vspace{-.9cm}
    
    \cvpresentation
    {Placed 3rd in Audubon Business Concept Pitch Plan, and 2nd in Audience Choice Award.} % Role
    {Yale School of Management Pre-MBA Program - Global Pre-MBA Leadership Program} % Title
    {2014 | Yale} % Location
    {} % Date(s)
    {\empty}
    {\empty}
    \vspace{-.9cm}
    
    \cvpresentation
    {Coordinate and plan events for increasing collaboration within department.} % Role
    {BME PhD Council - Social Chair} % Title
    {2016 --- 2017 | JHU} % Location
    {} % Date(s)
    {\empty}
    {\empty}
    \vspace{-.9cm}

    \cvpresentation
    {Led class of 16 individuals.} % Role
    {Alpha Kappa Psi - Class President} % Title
    {2012 --- 2014 | UCSD} % Location
    {} % Date(s)
    {\empty}
    {\empty}
    \vspace{-.9cm}
%---------------------------------------------------------
\end{cventries}
