%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Conference Presentations and Posters}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cvpresentation{NeurIPS}
    {Causal discovery from observational and
interventional data across multiple environments} % Title
    {New Orleans, USA} % Date(s)
    {Dec 2023} % Location
    {Adam Li, Amin Jaber, Elias Bareinboim}% Role
    {}
    \vspace{-0.4cm}
    
    \cvpresentation{CMStatistics}
    {Manifold random forests for decoding EEG data and estimating mutual information} % Title
    {Berlin, Germany} % Date(s)
    {Dec. 2023} % Location
    {Adam Li, et al.} % Role
    {}
    \vspace{-0.4cm}
    
    \cvpresentation{Society for Neuroscience}
    {Manifold Oblique Random Forests For Decoding EEG Signals Without Feature Engineering}
    {San Diego, USA}
    {Nov. 2022}
    {\textbf{Adam Li}, Ronan Perry, Chester Huynh, Jong Shin, Soo Kyung S. Kim, Jorge Gonzalez-Martinez, Sridevi V. Sarma and Joshua Vogelstein}
    {}
    \vspace{-0.4cm}  

    \cvpresentation{American Epilepsy Society}
    {Neural Fragility of the Intracranial EEG Network Decreases Intraoperatively after  Surgical Resection of the Epileptogenic Zone in Children with Epilepsy}
    {Chicago, USA}
    {Dec. 2021}
    {\textbf{Adam Li}, Patrick Myers, Chester Huynh, Nebras Warsi, Kristin M. Gunnarsdottir, Soo Kyung S. Kim, Viktor Jirsa, Sridevi V. Sarma and George M. Ibrahim}
    {}
    \vspace{-0.4cm}  
    
    \cvpresentation{American Epilepsy Society}
    {Neural Fragility as an EEG Marker of the Seizure Onset Zone}
    {Chicago, USA}
    {Dec. 2021}
    {Patrick Myers, \textbf{Adam Li}, C. Huynh, Z. Fitzgerald, I. Cajigas, D. Brusko, J. Jagid, A. Claudio, A. Kanner, J. Hopp, S. Chen, J. Haagensen, E. Johnson, W. Anderson, N. Crone, S. Inati, K. Zaghloul, J. Bulacio, J. Gonzalez-Martinez, S. V. Sarma}
    {}
    \vspace{-0.4cm}  
    
    \cvpresentation{Neuromatch 3.0 Conference}
    {Neural Fragility of Intracranial EEG Networks: Towards an EEG Fingerprint for the Seizure Onset Zone}
    {Baltimore, USA}
    {Oct. 2020}
    {\textbf{Adam Li}, C. Huynh, Z. Fitzgerald, I. Cajigas, D. Brusko, J. Jagid, A. Claudio, A. Kanner, J. Hopp, S. Chen, J. Haagensen, E. Johnson, W. Anderson, N. Crone, S. Inati, K. Zaghloul, J. Bulacio, J. Gonzalez-Martinez, S. V. Sarma}
    {}
    \vspace{-0.4cm}  
    
  \cvpresentation
    {IEEE Engineering in Medicine and Biology}%meeting
    {Automated classification of stereo-EEG contacts in white matter versus gray matter using recorded activity} % poster title
    {Montreal, Canada (virtual)} % Location
    {Jul. 2020} % Date(s)
    {\textbf{Adam Li}, Patrick Greene, Jorge Martinez-Gonzalez, Sridevi Sarma}%authors
    {}
    \vspace{-0.4cm}   
    
  \cvpresentation
    {IEEE Engineering in Medicine and Biology}%meeting
    {Towards Automatic Localization and Anatomical Labeling of Intracranial Depth Electrodes in Brain Images} % poster title
    {Montreal, Canada (virtual)} % Location
    {Jul. 2020} % Date(s)
    {\textbf{Adam Li}, Chester Huynh, Jorge Martinez-Gonzalez, Sridevi Sarma}%authors
    {}
    \vspace{-0.4cm}    
    
  \cvpresentation
    {Organization for Human Brain Mapping}%meeting
    {Semi-Automatic SEEG Localization and Interactive Neuroimage Visualization in Epilepsy Patients} % poster title
    {Montreal, Canada} % Location
    {June 23 - July 3, 2020} % Date(s)
    {\textbf{Adam Li}, Chester Huynh, Christopher Coogan, Sridevi Sarma}%authors
    {}
    \vspace{-0.4cm}    
    
  \cvpresentation
    {Organization for Human Brain Mapping}%meeting
    {MNE-BIDS: MNE-Python + BIDS = easy dataset interaction (Version 1.0.1)} % poster title
    {Montreal, Canada} % Location
    {June 23 - July 3, 2020} % Date(s)
    {Stefan Appelhoff, \textbf{Adam Li}, et al. - 10.5281/zenodo.3891836}%authors
    {}
    \vspace{-0.4cm}    
    
    \cvpresentation
    {AANS}%meeting
    {Identification of the Epileptogenic Zone from Intracranial Electrocorticography with a Novel Network Fragility Algorithm in Patients with Temporal-Lobe Epilepsy} % poster title
    {Virtual} % Location
    {Jun. 2020} % Date(s)
    {Iahn Cajigas, Damian Brusko, Angel Claudio, \textbf{Adam Li}, Sridevi Sarma, Andres Kanner, Jonathan Jagid}%authors
    {}
    \vspace{-0.4cm}  
    
  \cvpresentation
    {American Epilepsy Society}%meeting
    {Application of A Network Fragility Algorithm for the Identification of the Epileptogenic Zone from Intracranial Electrocorticography in Patients with Temporal-Lobe Epilepsy} % poster title
    {Baltimore, MD} % Location
    {Nov. 2019} % Date(s)
    {\textbf{Adam Li}, Iahn Cajigas, Damian Brusko, Angel Claudio, Andres Kanner, Jonathan Jagid, Sridevi Sarma}%authors
    {}
    \vspace{-0.4cm}  
    
  \cvpresentation
    {Workshop on Machine Learning and Computer Vision}%meeting
    {Using personalized brain models to augment datasets for deep learning} % poster title
    {Janelia, HHMI, USA} % Location
    {Apr. 2019} % Date(s)
    {\textbf{Adam Li}, Sridevi Sarma, Viktor Jirsa}%authors
    {}
    \vspace{-0.4cm}  
    
  \cvpresentation
    {Organization for Computational Neuroscience}%meeting
    {Integrating Large Brain Networks and Network Analysis to Understand The Epileptogenic Zone} % poster title
    {Seattle, WA} % Location
    {Jul. 2018} % Date(s)
    {\textbf{Adam Li}, Marmaduke Woodman, Sridevi Sarma, Viktor Jirsa}%authors
    {}
    \vspace{-0.4cm}   
  
  \cvpresentation
    {Advanced Course on Data Science \& Machine Learning}%meeting
    {Integrating Large Brain Networks and Network Analysis to Understand The Epileptogenic Zone} % poster title
    {Tuscany, Italy} % Location
    {Jul. 2018} % Date(s)
    {\textbf{Adam Li}, Sridevi Sarma, Viktor Jirsa}%authors
    {}
    \vspace{-0.4cm}  

  \cvpresentation
    {Clinical Neurophysiology}%meeting
    {T101. Use of a quantitative algorithm to help predict seizure lateralization in a patient with bitemporal epilepsy and responsive nerve stimulation} % poster title
    {Seattle, WA} % Location
    {2018} % Date(s)
    {Jennifer J. Haagensen, Stephanie Chen, Jennifer L. Hopp, \textbf{Adam Li}, Sridevi Sarma}%authors
    {}
    \vspace{-0.9cm}

\cvsection{Invited Talks}

    \cvpresentation
    {Johns Hopkins Neurodata Lab - Lab Meeting}%meeting
    {Robust Causal Discovery} % poster title
    {Baltimore, MD} % Location
    {08/26/2022} % Date(s)
    {\textbf{Adam Li}, A. Ribeiro, E. Bareinboim} % Role Location}%authors
    {}

    \cvpresentation
    {UCSF Epilepsy Center - Journal Club}%meeting
    {Neural Fragility as an EEG Marker of the Seizure Onset Zone} % poster title
    {San Francisco, CA} % Location
    {09/30/2021} % Date(s)
    {\textbf{Adam Li}, C. Huynh, Z. Fitzgerald, I. Cajigas, D. Brusko, J. Jagid, A. Claudio, A. Kanner, J. Hopp, S. Chen, J. Haagensen, E. Johnson, W. Anderson, N. Crone, S. Inati, K. Zaghloul, J. Bulacio, J. Gonzalez-Martinez, S. V. Sarma} % Role Location}%authors
    {}
    \vspace{-0.9cm}
    
%---------------------------------------------------------
\end{cventries}
