\cvsubsection{Work Experience}
\begin{cventries}
    \cvproject
    {PhD Software Engineering Intern at Uber} % Institution
    {Sep. 2022 --- Dec. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{Led research \& development of a causal machine learning model (applied to 100M+ samples) to dynamically match users with promotional campaigns demonstrating a potential \textbf{3-8\% increase in profit margins for USA Eats platform.}}
        \item{Developed solution to enable Python3.8+ in PySpark and SparkMagic Jupyter notebooks, enabling users to upgrade and reduce  technical debt in data science workflows with Python, Hive and Hadoop.}
      \end{cvitems}
    }
    \newline
    
    \cvproject
    {Co-Founder and CTO, Neurologic Solutions Corp.} % Institution
    {Sep. 2018 --- Dec. 2021} % Date(s)
    % {Neurologic Solutions is a pre-revenue company that aims to improve the diagnosis and treatment of patients with epilepsy by building a portfolio of smart EEG analytic software tools. }
    {
      \begin{cvitems} % Description(s) bullet points
        \item{Raised over \$600K to-date (Two NSF SBIR Phase I \$225k, Mayland Innovation Initiative \$150k, \$10K JHTV Pitch Competition).}
        \item{Filed provisional patents and full patents in the USA, European and Japan markets through collaboration with Johns Hopkins Technology Ventures (JHTV).}
        \item{Led product development of software product with team of 3 software engineers for helping clinicians localize the epileptogenic zone in epileptic patients (AWS infrastructure with Kubernetes and Flux, REST API, algorithm development, UX design and data engineering).}
        \item{Led \textbf{510k FDA} approval process with a team of 5 engineers, consultants and advisors involving risk analysis, software requirements, design specifications, and user-testing (unit testing, continuous integration, and software documentation).}
      \end{cvitems}
    }
    \newline

    \cvproject
    {Co-Founder, Biometrics Analytics} % Institution
    {Jun. 2012 --- Sep. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{Researched \& developed novel ways to evaluate Parkinson's Disease using biometric sensors and robust data analysis; led team in data acquisition of human data, data analysis and statistical analysis using MATLAB and Python.}
        \item{Led data acquisition of clinical data and full-body pose data from the Microsoft Kinect. Performed data analysis using machine learning and image processing algorithms (MATLAB, Python and C++).}
        \item{Raised over \$20,000 and obtained an IRB for a pilot clinical human study, resulting in the Gordon Fellowship Award for outstanding engineering leadership (awarded to 3 students/year at UCSD).}
        \item{Worked in a team of 4 for the Von Liebig NSF I-Corps Program and the NCIIA Entrepreneurship Program (~15\% acceptance rate) for startup incubation.}
      \end{cvitems}
    }
    % \newline
    \newline
    
    \cvproject
    {Data Processing Intern, West Health Institute 501(C)} % Institution
    {Jun. 2014 --- Jun. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{Wrote pymongo queries running on an event scheduler (Python, MongoDB) that provided computed features of game play and behavior for the clinical team to analyze behavior during experiments.}
        \item{Developed clinical web forms using HTML, CSS, JavaScript, which are then linked to an AWS server running MongoDB with Node.js (git and general version control).}
        \item{Built an Android application that created a custom launch screen for the clinical team with Java and XML.}
        \item{Researched and recommended technological improvements to data collection that could be incorporated into the analytics group at the institute for the treatment of Autism Spectrum Disorder.}
      \end{cvitems}
    }
    \newline
    
    \cvproject
    {Project Team Leader, West Health Institute 501(C)} % Institution
    {Jun. 2014 --- Jun. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{Wrote pymongo queries running on an event scheduler (Python, MongoDB) that provided computed features of game play and behavior for the clinical team to analyze behavior during experiments.}
        \item{Developed clinical web forms using HTML, CSS, JavaScript, which are then linked to an AWS server running MongoDB with Node.js (git and general version control).}
        \item{Built an Android application that created a custom launch screen for the clinical team with Java and XML.}
        \item{Researched and recommended technological improvements to data collection that could be incorporated into the analytics group at the institute for the treatment of Autism Spectrum Disorder.}
      \end{cvitems}
    }
    \newline
    
    \cvproject
    {Process Development Engineering Intern and College Ambassador, Genentech} % Institution
    {Aug. 2010 --- Aug. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{Collaborated with Genentech College Programs to improve online engagement by ~60\%, while coordinating events with directors and human resources that drew in over 200 attendees.}
        \item{Implemented a new batch control process using Rockwell Automation and PLCs to automate chromatography purification process (used SQL and Python).}
      \end{cvitems}
    }
    % \newline
 \end{cventries}